Progress Report

### 2023-09-20 Docs/ProgressReport.Rmd
adjust test sample of GLMMadaptive

- when fitting model with **random intercept + slope** on the same full training set: Error: vector memory exhausted (limit reached?)
- when fitting model with **only random intercept** on the same full training set: Error regarding a large coefficient value. One fix is to re-scale covariates. So I re-scaled minute index by dividing them by J, so the range is within (0, 1], and tried again. This fitting procedure took 20.72 minutes to finish
- Out-of-sample prediction took 12.18 minutes. About 0.007 minute per subject.

@@

```{r}
# up to 540
auc_t540_adglmm <- adglmm_pred_t540$newdata2 %>%
  mutate(sind=sind*J) %>%
  mutate(window = cut(sind, breaks = c(540, 780, 1020, 1260, 1440), 
                      labels = c("9am-1pm", "1pm-5pm", "5pm-9pm","9pm-12pm"), 
                      include.lowest = T))
auc_t540_adglmm <- split(auc_t540_adglmm, f=auc_t540_adglmm$window)
auc_t540_adglmm <- auc_t540_adglmm[1:3] %>% 
  lapply(function(x)performance(prediction(x$pred, x$Y), measure = "auc"))
auc_t540_adglmm <- lapply(auc_t540_adglmm, function(x){x@y.values[[1]]}) %>% unlist()

# up to 780
auc_t780_adglmm <- adglmm_pred_t780$newdata2 %>%
  mutate(sind=sind*J) %>%
  mutate(window = cut(sind, breaks = c(780, 1020, 1260, 1440), 
                      labels = c("1pm-5pm", "5pm-9pm","9pm-12pm"), 
                      include.lowest = T))
auc_t780_adglmm <- split(auc_t780_adglmm, f=auc_t780_adglmm$window)
auc_t780_adglmm <- auc_t780_adglmm[1:2] %>% 
  lapply(function(x)performance(prediction(x$pred, x$Y), measure = "auc"))
auc_t780_adglmm <- lapply(auc_t780_adglmm, function(x){x@y.values[[1]]}) %>% unlist()

# up to 1020
auc_t1020_adglmm <- adglmm_pred_t1020$newdata2 %>%
  mutate(sind=sind*J) %>%
  mutate(window = cut(sind, breaks = c(1020, 1260, 1440), 
                      labels = c("5pm-9pm","9pm-12pm"), 
                      include.lowest = T))
auc_t1020_adglmm <- split(auc_t1020_adglmm, f=auc_t1020_adglmm$window)
auc_t1020_adglmm <- auc_t1020_adglmm[1] %>% 
  lapply(function(x)performance(prediction(x$pred, x$Y), measure = "auc"))
auc_t1020_adglmm <- lapply(auc_t1020_adglmm, function(x){x@y.values[[1]]}) %>% unlist()

>>>>

- when fitting model with **random intercept + slope** on the same full training set (even after scaling covariates): Error: vector memory exhausted (limit reached?). 
- when fitting model with **only random intercept** on the same full training set: Error regarding a large coefficient value. One fix is to re-scale covariates. So I re-scaled minute index by dividing them by J, so the range is within (0, 1], and tried again. This fitting procedure took 20.72 minutes to finish
- Out-of-sample prediction took 12.18 minutes. About 0.007 minute per subject.
- I'd also exclude the subjects with failed Laplace approximation here. 
- Should I calculate AUC subject-wise?

@@

```{r}
# up to 540
auc_t540_adglmm <- adglmm_pred_t540$newdata2 %>%
  filter(!id %in% skip_id) %>%
  mutate(sind=sind*J) %>%
  mutate(window = cut(sind, breaks = c(540, 780, 1020, 1260, 1440), 
                      labels = c("9am-1pm", "1pm-5pm", "5pm-9pm","9pm-12pm"), 
                      include.lowest = T))
auc_t540_adglmm <- split(auc_t540_adglmm, f=auc_t540_adglmm$window)
auc_t540_adglmm <- auc_t540_adglmm[1:3] %>% 
  lapply(function(x)performance(prediction(x$pred, x$Y), measure = "auc"))
auc_t540_adglmm <- lapply(auc_t540_adglmm, function(x){x@y.values[[1]]}) %>% unlist()

# up to 780
auc_t780_adglmm <- adglmm_pred_t780$newdata2 %>%
  filter(!id %in% skip_id) %>%
  mutate(sind=sind*J) %>%
  mutate(window = cut(sind, breaks = c(780, 1020, 1260, 1440), 
                      labels = c("1pm-5pm", "5pm-9pm","9pm-12pm"), 
                      include.lowest = T))
auc_t780_adglmm <- split(auc_t780_adglmm, f=auc_t780_adglmm$window)
auc_t780_adglmm <- auc_t780_adglmm[1:2] %>% 
  lapply(function(x)performance(prediction(x$pred, x$Y), measure = "auc"))
auc_t780_adglmm <- lapply(auc_t780_adglmm, function(x){x@y.values[[1]]}) %>% unlist()

# up to 1020
auc_t1020_adglmm <- adglmm_pred_t1020$newdata2 %>%
  filter(!id %in% skip_id) %>%
  mutate(sind=sind*J) %>%
  mutate(window = cut(sind, breaks = c(1020, 1260, 1440), 
                      labels = c("5pm-9pm","9pm-12pm"), 
                      include.lowest = T))
auc_t1020_adglmm <- split(auc_t1020_adglmm, f=auc_t1020_adglmm$window)
auc_t1020_adglmm <- auc_t1020_adglmm[1] %>% 
  lapply(function(x)performance(prediction(x$pred, x$Y), measure = "auc"))
auc_t1020_adglmm <- lapply(auc_t1020_adglmm, function(x){x@y.values[[1]]}) %>% unlist()
